Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-04-08 manuscript.tex
Use polyhedron in abstract

\begin{abstract}
    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
    The standard method of determining the gravitational potential, through the use of a polyhedral potential model, is dependent on the shape model.
    Furthermore, accurate landing or low altitude operations requires an accurate knowledge of the surface topology. 
    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
    Range measurements of the surface are used to incrementally correct an initial shape estimate.
    This update procedure occurs in real time and provides a more accurate model of the asteroid shape.
    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
    The closed loop approach allows a spacecraft to approach and operate near an unknown asteroid while autonomously generating a surface shape model.
    We demonstrate this approach through a dynamic simulation about asteroid 4769 Castalia.
\end{abstract}

@@

In this paper, we consider the landing of a dumbbell model of a spacecraft onto an asteroid.
The dumbbell spacecraft consists of two masses connected by a massless rod and is a well-known representation of a multi body spacecraft.
Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
As a result, this simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.
In this section, we briefly review the polyhedron potential model and then present the derivation of the coupled dynamics of a dumbbell spacecraft about an asteroid.
Finally, we assume that the asteroid is much more massive than the spacecraft and it's motion is not affected by that of the spacecraft.
This assumption allows us to treat the motion of the vehicle independently from that of the asteroid. 
In this section we summarize the development of the polyhedron potential model and the derivation of the equations of motion of a rigid dumbbell spacecraft about an asteroid.

@@

\section{Asteroid Shape Modeling}

\subsection{Shape Reconstruction}

@@

\section{Expected Results and Significance}
This work will present an efficient method of reconstructing the shape of an asteroid from range measurements. 
The method allows for a real time approach to incrementally update a shape model of an asteroid.
Instead of performing a global update, each measurement is applied locally to the shape. 
This updated shape model is then used in a polyhedron potential model to enable a more accurate dynamic model near the asteroid.
This approach avoids the lengthy mapping phase of many spacecraft missions and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surface.

>>>>

\begin{abstract}
    Knowledge of the shape of an asteroid is crucial for spacecraft operations.
    The standard method of determining the gravitational potential, through the use of a polyhedron potential model, is dependent on the shape model.
    Furthermore, accurate landing or low altitude operations requires an accurate knowledge of the surface topology. 
    The typical approach to shape determination requires an extensive ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
    Instead, we present an efficient method for estimating the shape of an asteroid in real time.
    Range measurements of the surface are used to incrementally correct an initial shape estimate.
    This update procedure occurs in real time and provides a more accurate model of the asteroid shape.
    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
    The closed loop approach allows a spacecraft to approach and operate near an unknown asteroid while autonomously generating a surface shape model.
    We demonstrate this approach through a dynamic simulation about asteroid 4769 Castalia.
\end{abstract}

@@

In this paper, we consider the landing of a dumbbell model of a spacecraft onto an asteroid.
The dumbbell spacecraft consists of two masses connected by a massless rod and is a well-known representation of a multi body spacecraft.
Furthermore, the dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics. 
As a result, this simple model is useful to capture the main characteristics of a wide variety of spacecraft configurations.
Typically, spacecraft have mass concentrated in a central structure, referred to as the bus, which houses the command and control system, actuators, fuel, sensors etc. 
In addition, comparatively light-weight solar panels extend from the bus to provide electrical energy from solar radiation. 
As a result, the distributed mass of the spacecraft is captured with the dumbbell representation.
In this section, we briefly review the polyhedron potential model and then present the derivation of the coupled dynamics of a dumbbell spacecraft about an asteroid.
Finally, we assume that the asteroid is much more massive than the spacecraft and it's motion is not affected by that of the spacecraft.
This assumption allows us to treat the motion of the vehicle independently from that of the asteroid. 
In this section we summarize the basis of the polyhedron potential model and the derivation of the equations of motion of a rigid dumbbell spacecraft about an asteroid.

\subsection{Asteroid Shape Modeling}

@@

\section{Shape Reconstruction}

@@

\section{Conclusion}
This work will present an efficient method of reconstructing the shape of an asteroid from range measurements. 
The method allows for a real time approach to incrementally update a shape model of an asteroid.
Instead of performing a global update, each measurement is applied locally to the shape. 
This updated shape model is then used in a polyhedron potential model to enable a more accurate dynamic model near the asteroid.
This approach avoids the lengthy mapping phase of many spacecraft missions and enables a more responsive mission profile which allows the spacecraft to directly transition from arrival to surface operations.
Utilizing the updated shape model allows for real time feedback control as the dynamic model is continually updated to best match measurements of the surface.
